\LARGE \bf Sandhi: An open source alternative to LabVIEW

### 2014-01-19 paper.tex
grammatical fixes

\begin{figure}[ht!]
	\centering
	\includegraphics[width=90mm]{step_response.png}
	\caption{Step response plot for open loop csim block}
	\label{overflow}
\end{figure}

@@

LabVIEW has a great legacy and a lot of development and support has given by National Instruments. However for academic institutions and for educational purposes, a free and open source software is essential and Sandhi is an attempt to fill this void. Sandhi primarily focuses on control system applications but its framework is ready to extend it to newer paradigms. With its access to Scilab's rich computational engine, Sandhi can be extended from simple image processing filter blocks to complex backward propogation of neural networks. Keeping it open and free is necessary for community based development, software code quality, and enhanced learning.

>>>>

\begin{figure}[ht!]
	\centering
	\includegraphics[width=90mm]{step_response.png}
	\caption{Step response plot for open loop csim simulation}
	\label{overflow}
\end{figure}

@@

LabVIEW has a great legacy and a lot of development, support has been given by National Instruments. However, for academic institutions and for educational purposes, a free and open source software is essential and Sandhi is an attempt to fill this void. Sandhi primarily focuses on control system applications but its framework is ready to be extended it into newer paradigms. With its access to Scilab's rich computational engine, Sandhi can be extended from simple image processing filter blocks to complex backward propogation algorithms of neural networks. Keeping it open and free is necessary for community based development, high quality software code, and enhanced learning.
